### 2019-12-17 ic-journal/sos.tex

important theorems (\emph{rules}, \emph{ind} and \emph{cases}):

@@

  \item \emph{rules} is a conjunction of implications (each

@@

    same as the input term.
    In fact, the following formal versions of SOS rules are

@@

\item \emph{ind} is the induction principle for the relation
  (see Section~\ref{sec:multivariate} for the exact form and its application).
\item \emph{cases} is the so-called `cases' or `inversion' theorem for

@@

For instance, the following proposition needs the above \emph{cases} theorem:

>>>>

important theorems (\texttt{TRANS_rules}, \texttt{TRANS_ind} and \texttt{TRANS_cases}):

@@

  \item \texttt{TRANS_rules} is a conjunction of implications (each

@@

    same as the input term. In fact, the following formal versions of SOS rules are

@@

\item \texttt{TRANS_ind} is the induction principle for the relation
  (see Section~\ref{sec:multivariate} for its exact statement and an
  application in the proof of Proposition~\ref{prop:transFV}).
\item \texttt{TRANS_cases} is the so-called `cases' or `inversion' theorem for

@@

For instance, the following proposition requires \texttt{TRANS_cases}:
